---
title: "individual3"
author: "Felix Baez-Santiago"
date: "3/19/2021"
output: html_document
---
Part two: Tidying

```{r}
offClean2 <- offClean %>%
  pivot_longer(Rushing_ATT:Passing_INT, names_to = 'stat')
str(offClean2)
```

```{r}
ggplot(offClean2, aes(x = stat, y = value)) + geom_bar(stat = 'identity')
```

The passing yards and rushing yards have a significantly higher value than any other category.


```{r}
OK <- offClean %>%
  filter(Opponent_Opponent=='Oklahoma') %>%
  ggplot(aes(x=Name, y=Receiving_YDS)) + geom_point() + theme(axis.text.x = element_text(angle=90))
OK
OR <- offClean %>%
  filter(Opponent_Opponent=='Oregon') %>%
  ggplot(aes(x=Name, y=Receiving_YDS)) + geom_point() + theme(axis.text.x = element_text(angle=90))
OR
```
I think that Iowa did better against Oklahoma offensively than they did against Oregon because there are significantly more receiving yards per player in the Oklahoma game than there are in the Oregon one.


```{r}
bioClean2 <- bioClean %>%
  separate(Hometown, c('City', 'State', sep = ','))
States <- full_join(pivot_wider(offClean, Name), pivot_wider(defClean, Name))
States2 <- select(bioClean2, c(Name, State))
States <- left_join(States, States2, by = 'Name')
summary(factor(States$State))
```

```{r}
BrockP <- full_join(x = offClean, y = defClean)
BrockP2 <- BrockP %>%
  filter(Name == 'Purdy, Brock')
Team <- BrockP %>%
  filter(Name != 'Purdy, Brock')
ggplot(BrockP, aes(x = Opponent_Opponent, y = Rushing_TD)) + geom_bar(stat = 'identity')
ggplot(Team, aes(x = Opponent_Opponent, y = Rushing_TD)) + geom_bar(stat = 'identity')
```

Overall, Brock has more rushing touchdowns than the rest of the team on average


```{r}
def2019 <- read_excel('C:/Users/visma/Desktop/DS202/ds202_lab4/cyclonesFootball2019.xlsx', sheet='Defensive')
off2019 <- read_excel('C:/Users/visma/Desktop/DS202/ds202_lab4/cyclonesFootball2019.xlsx', sheet='Offensive')
```